Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-14 analyses/reproduce_analyses.Rmd
Display relative fitness plot of univariate adaptive landscape. This isn't in the main text of the manuscript, but its still a useful visualization.
Remove prior versions of univariate landscapes that tried to also include selection due to larval parasitoids.

```{r Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE, include=F}
# Get legend
AF_uni_legend <- get_legend(legend_only + theme(legend.position="top", legend.title.align = 0.5) + guides(color=guide_legend(title.position="top")))

# Make plots
AF_uni_plots <- plot_grid(NULL,
                          Diam_legend_only + theme(legend.position = "none",                         
                                             axis.title.y = element_blank(),
                                             axis.text.x = element_blank()),
                     pref_legend_only + theme(legend.position = "none",                          
                                             axis.title.y = element_blank(),
                                             axis.text.x = element_blank()) + xlab("Preference (SDs)"),
                     legend_only + theme(legend.position = "none",                         
                                             axis.title.y = element_blank()),
                       labels = c("","A", "B", "C"), hjust=0.06, vjust=0.1, 
                     ncol = 1, nrow=4, align='hv', rel_heights = c(0.5,1,1,1))

AF_uni_legend_plots <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x=0.15,y=0.4)
y_title_AF_uni_plots <- ggdraw() + draw_label("Mean larval survival", angle = 90, size=16)

AF_gradients <- plot_grid(y_title_AF_uni_plots, AF_uni_legend_plots, ncol=2, rel_widths = c(0.1,1))
AF_gradients
save_plot(filename = "UV_landscapes.pdf", plot = AF_gradients, base_height = 9, base_width = 7)
```

```{r Alt Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE, include=F}
# Get legend
AF_uni_legend <- get_legend(legend_only + theme(legend.title.align = 0.5))

# Make plots
AF_uni_plots <- plot_grid(NULL,
                          Diam_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
                                             axis.title.y = element_blank()), 
                                             #axis.text.y = element_blank(),
                                             #axis.text.x = element_text(size=10),
                                             #axis.title.x = element_text(size=11)),
                     pref_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
                                             axis.title.y = element_blank()), 
                                             #axis.text.y = element_blank(),
                                             #axis.text.x = element_text(size=10),
                                             #axis.title.x = element_text(size=11)),
                     legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
                                             axis.title.y = element_blank()), 
                                             #axis.text.y = element_blank(),
                                             #axis.text.x = element_text(size=10),
                                             #axis.title.x = element_text(size=11)),
                     #  labels = "AUTO", 
                     ncol = 2, align='hv')

AF_uni_legend_plots <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x=0.1, y=0.25) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
y_title_AF_uni_plots <- ggdraw() + draw_label("Mean larval survival", angle = 90)
AF_gradients <- plot_grid(y_title_AF_uni_plots, AF_uni_legend_plots, ncol=2, rel_widths = c(0.05,1))
AF_gradients
#AF_gradients <- plot_grid(AF_uni_legend, AF_uni_plots,  nrow = 2, rel_heights = c(0.1,1)) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
#AF_gradients

```{r Plot Univariate RF Landscapes, include=FALSE}

>>>>

# Replot univariate adaptive landscapes in terms of relative fitness

```{r Plot Univariate RF Landscapes}
